Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>

### 2023-09-29 index.Rmd
news

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | AI & digital&nbsp;humanities&nbsp;instructor </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

@@

### What I do  
<div style="text-align: justify; padding-left:1px"> 
I am a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, working on **language and culture dynamics**, using large corpora, machine learning, and human experiments. Recently I have been also working on, through various collaborations, on art history and creative industries and advising collaborative projects between involving academic and media industry partners.<br>
I defended my PhD in 2020, in linguistics at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R, stats & data visualization** and **AI**-related things (see [more here](https://datafigure.eu)).

@@

#### Publications

@@

@@

* Tillmann Ohm, Mar Canet Solà, Andres Karjus, Maximilian Schich. 2023. Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets | [preprint](https://arxiv.org/abs/2305.06809) | [interactive demo](https://collection-space-navigator.github.io/) | [code](https://github.com/Collection-Space-Navigator/CSN)

@@

- Wrote an opinion piece in ERR [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)
- Gave a number of interviews on artificial intelligence topics in Spring 2023 (in Estonian): [Äripäev radio](https://www.aripaev.ee/saated/2023/03/30/tehisintellekt-muudab-taiskasvanute-oppimist-ja-opikogemust), [TÜHI Eeter podcast](https://www.levila.ee/raadio/tuhi-eeter/kumb-on-arukam-kas-inimaru-voi-tehisaru), [PostimeesTV](https://haridus.postimees.ee/7722633/ekspert-eetris-andres-karjus-kas-chatgpt-hakkab-mojutama-meie-vaartusi-ja-kaitumist), BFM [Luna TV](https://www.youtube.com/watch?v=cXpNkDgfP7Y),  [Postimees](https://www.postimees.ee/7717736/tehisintellekti-abil-kodutoo-kirjutajaid-on-pea-voimatu-vahele-votta)
- News piece in [Pealinn](https://pealinn.ee/2022/09/29/vaata-millised-ettevotjad-saavad-tanavu-tunnustamise-osaliseks-ja-voidavad-auhinna/) on Tallinn city enterpreneurship prizes 2022, including me & colleagues for our media monitoring AI prototype in collaboration with AS Ekspress Grupp.
- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

>>>>

---
title: "Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analyst | AI&nbsp;&&nbsp;DH&nbsp;instructor </font>"
output: 
  html_document: 
    theme: spacelab
    toc: no
    toc_depth: 4  
    toc_float:
      collapsed: no
---

@@

### What I do  
<div style="text-align: justify; padding-left:1px"> 
I work on **language and culture dynamics**, using large corpora, machine learning & AI, and cognitive experiments. Recently I have been also working on, through various collaborations, on art history and creative industries, and advising collaborative projects between academia and the public and private sectors. I am affiliated as a research fellow at the [CUDAN](http://cudan.tlu.ee/) Cultural Data Analytics lab at Tallinn University, and at the [Estonian Business School](https://www.ebs.ee/en). <br>
I did my PhD at the [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) of the University of Edinburgh, on lexical dynamics and communicative need in language. <br>
I also occasionally do workshops on **R**, stats & data visualization and **AI**-related things (see [more here](https://datafigure.eu)).

@@

#### Publications (including in-review preprints)

* Andres Karjus. 2023. Machine-assisted mixed methods: augmenting humanities and social sciences with artificial intelligence | [preprint](https://arxiv.org/abs/2309.14379) | [data&code](https://github.com/andreskarjus/MachineAssistedMixedMethods)

@@

* Tillmann Ohm, Mar Canet Solà, Andres Karjus, Maximilian Schich. 2023. Collection Space Navigator: An Interactive Visualization Interface for Multidimensional Datasets. Proceedings of VINCI2023. | [proceedings version](https://www.vinci-symp.org/vinci_paper/vinci2023-t24.pdf) | [extended preprint](https://arxiv.org/abs/2305.06809) | [interactive demo](https://collection-space-navigator.github.io/) | [code](https://github.com/Collection-Space-Navigator/CSN)

@@

@@

- Wrote an opinion piece in ERR [Novaator](https://novaator.err.ee/1609007981/andres-karjus-tehisintellekt-seab-juba-sel-sugisel-koolid-sundvaliku-ette) on how generative AI will affect education in the near future (16.06.2023)
- Gave a number of interviews on artificial intelligence and education topics in 2023 (in Estonian):
[Kanal2 Õhtu](https://duoplay.ee/5826/ohtu?ep=749),
[Äripäev radio](https://www.aripaev.ee/saated/2023/03/30/tehisintellekt-muudab-taiskasvanute-oppimist-ja-opikogemust), 
[TÜHI Eeter podcast](https://www.levila.ee/raadio/tuhi-eeter/kumb-on-arukam-kas-inimaru-voi-tehisaru), [PostimeesTV](https://haridus.postimees.ee/7722633/ekspert-eetris-andres-karjus-kas-chatgpt-hakkab-mojutama-meie-vaartusi-ja-kaitumist), BFM [Luna TV](https://www.youtube.com/watch?v=cXpNkDgfP7Y),  [Postimees](https://www.postimees.ee/7717736/tehisintellekti-abil-kodutoo-kirjutajaid-on-pea-voimatu-vahele-votta)
- News piece in [Pealinn](https://pealinn.ee/2022/09/29/vaata-millised-ettevotjad-saavad-tanavu-tunnustamise-osaliseks-ja-voidavad-auhinna/) on Tallinn city enterpreneurship prizes 2022, including me & colleagues for our media monitoring AI prototype in collaboration with AS Ekspress Grupp.
- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.
